Soundness Proofs for Iterative Deepening

### 2016-08-24 oopsla-16/proof/convergence.tex
oopsla proof: address camreadies

The contrapositive statement offers more structure for an easier proof\footnote{
For the reader who likes to avoid non-constructive proofs, % \cite{vargomax}, % TODO CAMREADY: uncomment
note that we are using the constructive contrapositive direction:
Theorem~\ref{thm:convergence} is $A \rightarrow B$ and Theorem~\ref{thm:totalverif} is $\neg B \rightarrow \neg A$.}:

@@

It would be straightforward to show that any other data races in $t_{\alpha{}(i+1)}'$, which would be discovered in this interleaving,
could be reordered to after $\ppothers{\mathcal{I}}{\alpha}{i}'$,
eventually transforming $t_{\alpha{}(i+1)}'$ to contain no conflicting memory accesses but $\ppinstr{\mathcal{I}}{\alpha}{i}$ itself.
Unfortunately, $\mathcal{J}$ is not necessarily reachable, as $\ppothers{\mathcal{I}}{\alpha}{i}'$ still includes any data-race PPs from $\ppothers{\mathcal{I}}{\alpha}{i}$,
which were ordered after $\pai$ in $\mathcal{I}$ and hence not covered by the inductive assumption.
Hence, we must perform the same ``coalescing'' for each thread in $\ppothers{\mathcal{I}}{\alpha}{i}'$ that we did for $\alpha$,
which we will abbreviate:
\[
	\mathcal{K} = [..., (\tai \cup t_{\alpha{}(i+1)}', \paj), \coalesce{\ppothers{\mathcal{I}}{\alpha}{i}'} ]
\]
For each other thread $\beta$, $\coalesce{\ppothers{\mathcal{I}}{\alpha}{i}'}$ will contain a single transition,
starting with the first instruction of $\beta$'s corresponding transition in $\ppothers{\mathcal{I}}{\alpha}{i}$,
and ending with the next sync API PP in $\beta$, which we'll call $\pbk$.
Again, the only certainly-executed instruction by $\alpha$ after $\tai$ is $\ppinstr{\mathcal{I}}{\alpha}{i}$.
It is even possible that neither $\ppinstr{\mathcal{I}}{\alpha}{i}$ nor any other instruction by thread $\alpha$ will conflict with any other thread,
until a different data race PP between two other threads is discovered.
% TODO CAMREADY
%as shown in Figure~\ref{fig:threethreads}.

>>>>

The contrapositive statement offers more structure for an easier proof\footnote{
For the reader who likes to avoid non-constructive proofs \cite{vargomax},
note that we are using the constructive contrapositive direction:
Theorem~\ref{thm:convergence} is $A \rightarrow B$ and Theorem~\ref{thm:totalverif} is $\neg B \rightarrow \neg A$.}:

@@

It would be straightforward to show that any other data races in $t_{\alpha{}(i+1)}'$, which would be discovered in this interleaving,
could be reordered to after $\ppothers{\mathcal{I}}{\alpha}{i}'$,
eventually transforming $t_{\alpha{}(i+1)}'$ to contain no conflicting memory accesses but $\ppinstr{\mathcal{I}}{\alpha}{i}$ itself.
Unfortunately, $\mathcal{J}$ is not necessarily reachable, as $\ppothers{\mathcal{I}}{\alpha}{i}'$ still includes any data-race PPs from $\ppothers{\mathcal{I}}{\alpha}{i}$,
which were ordered after $\pai$ in $\mathcal{I}$ and hence not covered by the inductive assumption.
Hence, we must perform the same ``coalescing'' for each thread in $\ppothers{\mathcal{I}}{\alpha}{i}'$ that we did for $\alpha$,
which we will abbreviate:
\[
	\mathcal{K} = [..., (\tai \cup t_{\alpha{}(i+1)}', \paj), \coalesce{\ppothers{\mathcal{I}}{\alpha}{i}'} ]
\]
For each other thread $\beta$, $\coalesce{\ppothers{\mathcal{I}}{\alpha}{i}'}$ will contain a single transition,
starting with the first instruction of $\beta$'s corresponding transition in $\ppothers{\mathcal{I}}{\alpha}{i}$,
and ending with the next sync API PP in $\beta$, which we'll call $\pbk$.
Again, the only certainly-executed instruction by $\alpha$ after $\tai$ is $\ppinstr{\mathcal{I}}{\alpha}{i}$.
It is even possible that neither $\ppinstr{\mathcal{I}}{\alpha}{i}$ nor any other instruction by thread $\alpha$ will conflict with any other thread,
until a different data race PP between two other threads is discovered.
%as shown in Figure~\ref{fig:threethreads}.
